---
title: "Intro"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Intro}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(carbonFootprintR)
library(tidyverse)
```

This vignette serves as an example on how to use the various functions in this package.

For the purposes of this example we will use the data set included in this package called `invite_locations_list`.But since the data set is a data frame we will first have to convert this into a character vector.

Let's load that into memory using the command `pull`.
```{r}
locations <- invite_locations_list %>% pull
```

Next, let's add in the latitude (lat) and longitude(lon) for our people. In order to accomplish this, we will use the `coordinateGetter` function, which uses an openstreetmap API service. For the purposes of this vignette, I will use my account key, but you please get your own free key at https://developer.mapquest.com https://opencagedata.com/pricing.

```{r}
returnDF <- coordinateGetter(address = head(locations), osmKey = "QkAXkFcY9Yo5DUulr92JObQ09ym7RPv4")
```

## and now map to nearest airports
withAirports <- airportMatcher(returnDF)

## and now plot those vs London
df1 <- returnDF %>% select(lon, lat) %>% na.exclude(.)

chartMaker(lat1 = rep(51.1638229, nrow(df1)),
           lon1 = rep(0.1312621, nrow(df1)),
           lat2 = df1$lat,
           lon2 = df1$lon,
           color = "purple",
           lwd = 0.8)

## and get the footprint
# footprintGetter(from = "FNL", to = "LHR", class = "economy", API = "d29a6f1481b5365611fb708d")

withAirports$airport %>% map(~safely(footprintGetter)(from = .x, to = "LHR", 
                             class = "economy", API = "d29a6f1481b5365611fb708d")) -> footprints
footprints %>% map("error")

footprints %>% map_dfr("result") %>% summarize(cost = sum(cost_sek))

allFlights <- footprints %>% map_dfr("result") %>% 
  select(from, to) %>% unite(both, from, to, sep = "%2C") %>% 
  bind_cols(footprints %>% map_dfr("result") %>% 
              select(from, to) %>% unite(both, to, from, sep = "%2C")) %>% 
  unlist %>% paste(collapse = "%2C")

paste0("https://www.goclimateneutral.org/flight_offsets/new?offset_params=economy%2C", 
       allFlights, '&locale="en"') %>% cat

  https://api.exchangeratesapi.io/latest?symbols=USD,GBP
